Model LF

### 2022-10-06 max_dp endogen stød.Rmd
commit

```{r}
###Gengivelse af stød til model
max_dp_01b = Shock_1b$simulation$max_dp
wage_01b = Shock_1b$simulation$wage
komp_r_01b = Shock_1b$simulation$komp_r
part_01b = Shock_1b$simulation$part
yk_ds_01b = Shock_1b$simulation$yk_ds
pc_ds_01b = Shock_1b$simulation$pc_ds
wage_ds_t_01b = Shock_1b$simulation$wage_ds_t
ur_ds_01b = Shock_1b$simulation$ur_ds

@@

>>>>

```{r}
###Gengivelse af stød til model
max_dp_01b = Shock_1b$simulation$max_dp
wage_01b = Shock_1b$simulation$wage
komp_r_01b = Shock_1b$simulation$komp_r
part_01b = Shock_1b$simulation$part
yk_ds_01b = Shock_1b$simulation$yk_ds
pc_ds_01b = Shock_1b$simulation$pc_ds
wage_ds_t_01b = Shock_1b$simulation$wage_ds_t
ur_ds_01b = Shock_1b$simulation$ur_ds
emp_01b = Shock_1b$simulation$emp
yd_hk_ds_01b = Shock_1b$simulation$yd_hk_ds

nl_g_01b = Shock_1b$simulation$nl_g

@@

plot(((dp_person_01b - dp_person_00) / dp_person_00), col= "black", xlab= "Year", ylab= "% Change in avg income insurance");
legend("top", legend=c("income insurance"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((komp_r_01b - komp_r_00) / komp_r_00), col= "black", xlab= "Year", ylab= "% Change in compensation rate");
legend("top", legend=c("compensation rate"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

plot(((nl_g_01b - nl_g_00)), col= "black", xlab= "Year", ylab= "Change in government net lending");
legend("top", legend=c("government net lending"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((yd_hk_ds_01b - yd_hk_ds_00) / yd_hk_ds_00), col= "black", xlab= "Year", ylab= "% Change in households disposable income");
legend("top", legend=c("households disposable income"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

plot(((yk_ds_01b - yk_ds_00) / yk_ds_00), col= "black", xlab= "Year", ylab= "% Change in gdp");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((emp_01b - emp_00) / emp_00), col= "black", xlab= "Year", ylab= "% Change in employment");
legend("top", legend=c("Employment"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

plot(((yk_ds_01b - yk_ds_00) / yk_ds_00), col= "black", xlab= "Year", ylab= "% Change in gdp");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((emp_01b - emp_00) / emp_00), col= "black", xlab= "Year", ylab= "% Change in employment");
legend("top", legend=c("Employment"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```
